\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-30 metatheory-condensed.tex
Removing bWtau

    (* s[@₁@]  : {} | {} *)
    - o[@₁@]  = μ+ {} s[@₁@] ⋆ : 𝕃{ty : 𝕎τ[@₁@]}
    (* s[@₂@]  : {ty : 𝕎τ[@₁@]} | [ty : 𝕌; bool : ty; ...] *) 
    - o[@₂@]  = μ+ o[@₁@] s[@₂@] ⋆ : 𝕃{ty : 𝕎τ[@₁@]; tm : 𝕎τ[@₂@]}
    (* s[@₃@][@₁@]  : {ty : 𝕎τ[@₁@]; tm : 𝕎τ[@₂@]}
            | [ty : 𝕌; ... ; tm : 𝕌; tvar : tm; ...] *)
    - o[@₃@][@₁@]  = μ+ o[@₂@] s[@₃@] ([@μ@]+ ..) : 𝕃{ty : 𝕎τ[@₁@]; tm : 𝕎τ[@₂@]; subst' : 𝕃(RecSig)}
    (* s[@₃@] : {ty : 𝕎τ[@₁@]; tm : 𝕎τ[@₂@]; subst' : 𝕃(RecSig)} 
          | [ty : 𝕌; ... ; tm : 𝕎τ[@₂@]; subst' : 𝕃(RecSig)] *)
    - o[@₃@] = μ+ o[@₃@][@₁@] s[@₃@] (λ (Wrec ..)) : 𝕃{ty : 𝕎τ[@₁@]; tm : 𝕎τ[@₂@]; subst' : 𝕃(RecSig); subst : tm → nat → tm → tm}

    (* s[@₄@] : {ty : 𝕎τ[@₁@]; ... subst : tm → nat → tm → tm } 
          | [.. ; tm : 𝕌; tvar : nat → tm; .. subst : tm → nat → tm → tm] *)
    - o[@₄@] = μ+ o[@₃@] s[@₄@] [@("tvar"~0)@] : 𝕃{ty : 𝕎τ[@₁@]; ... t[@₁@] : [@\TyS{"tvar"~0}@]}

    (* s[@₅@] : {ty : 𝕎τ[@₁@]; tm : 𝕎τ[@₂@]; subst : 𝕃(RecSig); t1 : [@\TyS{"tvar"~0}@]} 
          | [ty : 𝕌; tm : 𝕌; subst : 𝕃(RecSig); t1 : [@\TyS{"tvar"~0}@]] *)
    - o[@₅@] = μ+ o[@₄@] s[@₅@] .. : 𝕃{ ... }
  \end{lstlisting}

@@

Each hiding comment corresponds to the textual-aligned sealing derivation on RHS. For legibility, curly brackets indicate a signature (omitting sealing at type level for readability) and square bracket indicate a nested $\Sigma$-type, corresponding to sealing judgment $\goodSeal{}{s}{\sigma}{A}$.

>>>>

    (* s[@₁@]  : {} | {} *)
    - o[@₁@]  = μ+ {} s[@₁@] [@$W\tau_1$@] : 𝕃{ty : [@$\TyS{W\tau_1}$@]}
    (* s[@₂@]  : {ty : [@$\TyS{W\tau_1}$@]} | [ty : 𝕌; bool : ty; ...] *) 
    - o[@₂@]  = μ+ o[@₁@] s[@₂@] [@$W\tau_2$@] : 𝕃{ty : [@$\TyS{W\tau_1}$@]; tm : [@$\TyS{W\tau_2}$@]}
    (* s[@₃@][@₁@]  : {ty : [@$\TyS{W\tau_1}$@]; tm : [@$\TyS{W\tau_2}$@]}
            | [ty : 𝕌; ... ; tm : 𝕌; tvar : tm; ...] *)
    - o[@₃@][@₁@]  = μ+ o[@₂@] s[@₃@] ([@μ@]+ ..) : 𝕃{ty : [@$\TyS{W\tau_1}$@]; tm : [@$\TyS{W\tau_2}$@]; subst' : 𝕃(RecSig)}
    (* s[@₃@] : {ty : [@$\TyS{W\tau_1}$@]; tm : [@$\TyS{W\tau_2}$@]; subst' : 𝕃(RecSig)} 
          | [ty : 𝕌; ... ; tm : [@$\TyS{W\tau_2}$@]; subst' : 𝕃(RecSig)] *)
    - o[@₃@] = μ+ o[@₃@][@₁@] s[@₃@] (λ (Wrec ..)) : 𝕃{ty : [@$\TyS{W\tau_1}$@]; tm : [@$\TyS{W\tau_2}$@]; subst' : 𝕃(RecSig); subst : tm → nat → tm → tm}

    (* s[@₄@] : {ty : [@$\TyS{W\tau_1}$@]; ... subst : tm → nat → tm → tm } 
          | [.. ; tm : 𝕌; tvar : nat → tm; .. subst : tm → nat → tm → tm] *)
    - o[@₄@] = μ+ o[@₃@] s[@₄@] [@("tvar"~0)@] : 𝕃{ty : [@$\TyS{W\tau_1}$@]; ... t[@₁@] : [@\TyS{"tvar"~0}@]}

    (* s[@₅@] : {ty : [@$\TyS{W\tau_1}$@]; tm : [@$\TyS{W\tau_2}$@]; subst : 𝕃(RecSig); t1 : [@\TyS{"tvar"~0}@]} 
          | [ty : 𝕌; tm : 𝕌; subst : 𝕃(RecSig); t1 : [@\TyS{"tvar"~0}@]] *)
    - o[@₅@] = μ+ o[@₄@] s[@₅@] .. : 𝕃{ ... }
  \end{lstlisting}

@@

Each hiding comment corresponds to the textual-aligned sealing derivation on RHS. For readability, RHS is informal---curly brackets indicate a signature (omitting sealing at type level) and square bracket indicate a nested $\Sigma$-type, corresponding to sealing judgment $\goodSeal{}{s}{\sigma}{A}$.
